### 2019-06-08 doc/chapters/trying_verify_checktx.tex
more text

It takes too much time to do it and after some discussion, we decided to extract only the parts of the code that are needed for checkTransaction.

The extracted code has more than 1500 lines.
After running Stainless on it, it throws a really huge bunch of errors about what Stainless can not reason about.
And after fixing some of those errors there appear new ones as we can see in the next chapter.
This would require to change nearly everything of the extracted code.

We arrived at the decision that we need a smaller part to verify.
We have chosen to verify the addition with zero of Bitcoin-Ss CurrencyUnit class as described in the next chapter.

>>>>

After integrating Stainless in Bitcoin-S there are many errors.
It takes too much time to fix them all so it should be easier to extract the classes needed for checkTransaction.

The extracted code has more than 1500 lines.
After running Stainless on it, it still throws a huge bunch of errors about what Stainless can not reason about.
After fixing some of those errors there appear new ones.
So this would require to change nearly everything of the extracted code.

Lets adjust the property from the \nameref{property_1} to the \nameref{property_2}, because there is not enough time to fix all this errors and write the verification.
This is way less interesting to verify but gives still many insights in what needs to be done to verify some parts of Bitcoin-S and other source code.

So lets look at the \nameref{property_2}.
